---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SummarizeCFromN

## Contents

### Folders:

*R:*  Contains the .R file for the function contained in the package

*man:* Contains documentation created by roxygen 

*tests:* Contains the testing code for the function in the package


### Files:

*.Rbuildignore:* This specifies untracked files to be deliberately ignored by Git.

*.gitignore:* This specifies untracked files to be deliberately ignored by Git.

*DESCRIPTION* This description file includes information regarding usage, required packages for functionality, and author information.

*LICENSE/LICENSE.md:* This details the licensing information.


*NAMESPACE:* This is a file generated by roxygen that specifies the functions in the package to be exported.

*NEWS.md:* This is a file that documents changes made to the package.

*README.Rmd/README.md:* This file! This contains information about the nature of the package, its contents, the aims of the project, and example usage.

*SummarizeNFromC.Rproj:* Contains the project options and can be used as a shortcut for opening the project directly from the file system.


# Overview

<!-- badges: start -->
<!-- badges: end -->

The goal of SummarizeNFromC is to output a tibble containing the mean, range, and standard deviation of some numerical object as sorted into some category. This function and package is part of the STAT 545B assignments B1 and B2, respectively.

## Installation and how to run code

### Installation

This package is not released on CRAN. With this, you can use the devtools package to install straight from this repository.
```{r}
devtools::install_github("AFishyButler/SummarizeNFromC")
```

### Running the code

Once installed, all code can be executed in RStudio from either a new or existing project.

## Example

This is a basic example which shows the basic functionality of the package: a tibble output containing the mean, range, and standard deviation of the diameter of a tree dependent on cultivar.
```{r example}
suppressPackageStartupMessages(library(datateachr))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(magrittr))
suppressPackageStartupMessages(library(SummarizeCFromN))

(summarize_N_from_C (vancouver_trees, cultivar_name , diameter ))
```

This function is compatible with any dataframe so long as one object is of character class and the other is numerical.
